---
title: "NY_NOAA"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
library(dplyr)
```

```{r}
library(p8105.datasets)
data("ny_noaa")
```

1. Tidy data

2. To reduce the size of dataset, in problem 2, I determine to select samples from this dataset to solve problem 2, selection standards are as followed:
* Only focus on data in 2007
* Only focus on days when precipitation, snowfall, snow depth, maximium temperature and minimium temperature are not empty.
* Only focus on days when precipitation, snowfall and snow depth are not zero.

3. The goal to select this sample is to show tmax vs tmin in 2007 when there are precipitation, snowfall and snow depth.
```{r}
ny_noaa = ny_noaa %>% 
  janitor::clean_names() %>% 
  drop_na(prcp) %>% 
  drop_na(snow) %>% 
  drop_na(snwd) %>% 
  drop_na(tmax) %>% 
  drop_na(tmin)  %>% 
  filter(prcp != 0 & snow != 0 & snwd != 0) %>% 
  # Unify the unit
  mutate(
    prcp = prcp/10,
    # change the unit of precipitation from tenths of mm to mm for later calculation
    tmax = as.numeric(tmax)/10,
    tmin = as.numeric(tmin)/10
    # change the unit of minimum and maximum temperature from tenths of degrees C to degrees C for later calculation
  ) %>%  #Separate date into year, month, day
  separate(date,into = c("year","month","day"),sep = "-") %>% 
  mutate(
     month = recode(month, "01" = "January",
                  "02" = "February",
                  "03" = "March",
                  "04" = "April",
                  "05" = "May",
                  "06" = "June",
                  "07" = "July",
                  "08" = "Augest",
                  "09" = "September",
                  "10" = "October",
                  "11" = "November", 
                  "12" = "December"
                  )
     )  %>% 
  filter(year == 2007)
```

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}

```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}

```

### Chart C

```{r}

```

